---
title: Risk Models Development Process
author: Jakub Szotek
date: November, 2019
fontsize: 9pt
output:
  beamer_presentation:
    colortheme: seahorse
    fig_height: 6
    fonttheme: serif
    keep_tex: yes
    slide_level: 3
    theme: Warsaw
    toc: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=58)
library(knitr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(DescTools)
require(caTools)
```

# 1. Data Preparation
### Data Preparation
  + Model population
  + Observation window
  + Observation level
  + Review of data systems
  + Source data
  
### Load data
```{r}
Data <- read.csv('https://raw.githubusercontent.com/jakubszotek/Presentations/master/Risk%20Models%20Development%20Process/Data/Data.csv')
```

### View data
```{r}
print(head(Data,4), digits = 2, row.names = FALSE)
```

# 2. Analysis of risk parameters
### All headers
```{r, echo = TRUE}
sapply(Data, class)
```

### Default variable
```{r, echo = TRUE}
head(Data,10) %>% select(Default_date, Default)
```

### Risk drivers
  + Types of drivers:
    + Demographic
    + Financial
    + Behavioural
    + Macroeconomic
  + Types of data:
    + Numerical
    + Boolean
    + Categorical
    
### Risk drivers
```{r, eval = FALSE}
Drivers <- Data %>% select(-Date_of_data,-Default_date)
print(head(Drivers,5), digits = 2, row.names = FALSE)
```

### Risk drivers
```{r, echo = FALSE}
Drivers <- Data %>% select(-Date_of_data,-Default_date)
print(head(Drivers,5), digits = 2)
```

### Single Factor Analysis - Univariate
  + We exclude all variables having more than 10% of missing values
  + Is there enough variance for each variable?
```{r}
var_summary <- summary(Drivers %>% select(Country, Industry,
                                          Length_of_business,
                                          Total_assets,
                                          Financial_leverage,
                                          Credit_limit,
                                          EDF,
                                          GDP_growth))
```

### Single Factor Analysis - Univariate
```{r, echo = FALSE}
var_summary[,1:5]
```

### Single Factor Analysis - Univariate
```{r, echo = FALSE}
var_summary[,6:8]
```

### Exclusions
+ Financial_leverage has 158 N/A's out of 1000 observations (15.8%)
```{r}
Drivers_1 = subset(Drivers, select=-c(Financial_leverage))
print(head(Drivers_1,5), digits = 2, row.names = FALSE)
```

### Further modifications
  + Handling outliers
  + Dealing with missing values if needed
  + Transformations:
    + exponential
    + logarithmic
    + polynomial
    
### Single Factor Analysis - Bivariate - Country
  + We check the relationship between risk drivers and default
```{r, echo = TRUE}
country_group <- Data %>% group_by(Country) %>%
  summarise(default_rate = mean(Default),count = n())
print(country_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Country
```{r, eval = FALSE}
ggplot(data=country_group, aes(x=Country, y=default_rate,
                               group=1)) +
    geom_bar(aes(x=Country, y=count/800),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 800,
                                           name = "count"))
```

### Single Factor Analysis - Bivariate - Country
```{r, echo = FALSE}
plot_country <- ggplot(data=country_group, aes(x=Country, y=default_rate, group=1)) +
    geom_bar(aes(x=Country, y=count/800),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 800, name = "count"))
plot_country
```

### Single Factor Analysis - Bivariate - Country
  + Switch from categorical variable Country to boolean Country_PL
  + Is this in line with common sense and expectations?
  + What is the expected impact of the variable on the final model?
  
### Single Factor Analysis - Bivariate - Country
```{r}
Drivers_2 <- Drivers_1
Drivers_2$Country_PL <- (Drivers_1$Country == "PL")*1
```

### Single Factor Analysis - Bivariate - Country
```{r, echo = FALSE}
print(head(subset(Drivers_2, select=-c(Customer_ID)),7), digits = 2, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Country
We remove the variable Country now
```{r, eval = FALSE}
Drivers_2 <- subset(Drivers_2, select=-c(Country))
print(head(Drivers_2,7), digits = 2, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Country
We remove the variable Country now
```{r, echo = FALSE}
Drivers_2 <- subset(Drivers_2, select=-c(Country))
print(head(subset(Drivers_2, select=-c(Customer_ID)),7), digits = 2)
```

### Single Factor Analysis - Bivariate - Industry
```{r, echo = TRUE}
industry_group <- Data %>% group_by(Industry) %>%
  summarise(default_rate = mean(Default),count = n())
print(industry_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Industry
```{r, eval = FALSE}
ggplot(data=industry_group, aes(x=Industry, y=default_rate,
                                group=1)) +
    geom_bar(aes(x=Industry, y=count/800),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 800,
                                           name = "count"))
```

### Single Factor Analysis - Bivariate - Industry
```{r, echo = FALSE}
plot_industry <- ggplot(data=industry_group, aes(x=Industry, y=default_rate, group=1)) +
    geom_bar(aes(x=Industry, y=count/800),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 800, name = "count"))
plot_industry
```

### Single Factor Analysis - Bivariate - Industry
  + Switch from categorical variables Industry $\in$ {A, B} to boolean Industry_AB
  + Is this in line with common sense and expectations?
  + What is the expected impact of the variable on the final model?

### Single Factor Analysis - Bivariate - Industry
```{r, eval=FALSE}
Drivers_3 <- Drivers_2
Drivers_3$Industry_AB <- (Drivers_2$Industry %in% c("A","B"))*1
print(head(subset(Drivers_3, select=-c(Customer_ID)),7),
      digits = 2, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Industry
```{r, echo=FALSE}
Drivers_3 <- Drivers_2
Drivers_3$Industry_AB <- (Drivers_2$Industry %in% c("A","B"))*1
print(head(subset(Drivers_3, select=-c(Customer_ID)),7),
      digits = 2, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Industry
```{r, echo = FALSE}
Drivers_3 <- subset(Drivers_3, select=-c(Industry))
print(head(subset(Drivers_3, select=-c(Customer_ID)),7), digits = 2, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Length_of_business
Let's bucket the data by year
```{r, echo = FALSE}
Data$Length_of_business_Floor <- floor(Data$Length_of_business)
length_group <- Data %>% group_by(Length_of_business_Floor) %>% summarise(default_rate = mean(Default),count = n())
print(length_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Length_of_business
Let's cut the dataset in 11 and put everything longer than that into one group
```{r, echo = FALSE}
Data$Length_of_business_Floor[Data$Length_of_business_Floor >= 11] <- 11
length_group <- Data %>% group_by(Length_of_business_Floor) %>% summarise(default_rate = mean(Default),count = n())
print(length_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Length_of_business
```{r, eval = FALSE}
ggplot(data=length_group, aes(x=Length_of_business_Floor,
                              y=default_rate, group=1)) +
    geom_bar(aes(x=Length_of_business_Floor, y=count/400),
             stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 400,
                                           name = "count"))
```

### Single Factor Analysis - Bivariate - Length_of_business
 + Is this relation in line with logic?
```{r, echo = FALSE}
plot_length <- ggplot(data=length_group, aes(x=Length_of_business_Floor, y=default_rate, group=1)) +
    geom_bar(aes(x=Length_of_business_Floor, y=count/400),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 400, name = "count"))
plot_length
```

### Single Factor Analysis - Bivariate - Total_assets
```{r, eval=FALSE}
Data$Total_assets_Floor <- floor(Data$Total_assets)
assets_group <- Data %>% group_by(
  Total_assets_Floor) %>% summarise(
    default_rate = mean(Default),count = n())
print(assets_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Total_assets
```{r, echo=FALSE}
Data$Total_assets_Floor <- floor(Data$Total_assets)
assets_group <- Data %>% group_by(Total_assets_Floor) %>% summarise(default_rate = mean(Default),count = n())
print(assets_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Total_assets
Let's cut the dataset in 8 and put everything longer than that into one group
```{r, echo = FALSE}
Data$Total_assets_Floor[Data$Total_assets_Floor >= 8] <- 8
assets_group <- Data %>% group_by(Total_assets_Floor) %>% summarise(default_rate = mean(Default),count = n())
print(assets_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Total_assets
```{r, eval = FALSE}
ggplot(data=assets_group, aes(x=Total_assets_Floor, y=default_rate,
                              group=1)) +
    geom_bar(aes(x=Total_assets_Floor, y=count/500),
             stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 500,
                                           name = "count"))
```

### Single Factor Analysis - Bivariate - Total_assets
```{r, echo = FALSE}
plot_assets <- ggplot(data=assets_group, aes(x=Total_assets_Floor, y=default_rate, group=1)) +
    geom_bar(aes(x=Total_assets_Floor, y=count/500),stat="identity",
             fill="tan1", colour="sienna3")+
    geom_line() +
    geom_point()+
    scale_y_continuous(name = waiver(),
                       sec.axis = sec_axis(~ . * 500, name = "count"))
plot_assets
```

```{r, include = FALSE}
temp <- Data$Credit_limit * 4
temp2 <- floor(temp)
temp3 <- temp2 / 4
temp3[temp3 >= 1.25] <- 1.25
Data$Credit_limit_Floor <- temp3
rm(temp,temp2,temp3)
```

### Single Factor Analysis - Bivariate - Credit_limit
```{r, echo = FALSE}
limit_group <- Data %>% group_by(Credit_limit_Floor) %>% summarise(default_rate = mean(Default),count = n())
print(limit_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Credit_limit
```{r, echo = FALSE}
plot_limit <- ggplot(data=limit_group, aes(x=Credit_limit_Floor, y=default_rate, group=1)) +
  geom_bar(aes(x=Credit_limit_Floor, y=count/500),stat="identity",
           fill="tan1", colour="sienna3")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . * 500, name = "count"))
plot_limit
```

### Single Factor Analysis - Bivariate - Expected Default Frequency
EDF is a variable common to all debtors dependent on year
```{r}
EDF_group <- Data %>% group_by(Date_of_data) %>%
  summarise(default_rate = mean(Default), EDF = mean(EDF),
            count = n())
print(EDF_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - Expected Default Frequency
```{r, echo = FALSE}
plot_edf <- ggplot(data=EDF_group, aes(x=Date_of_data, y=default_rate, group=1)) +
  geom_point()+
  geom_line(aes(x=Date_of_data, y=EDF * 10, group=1), col="Red")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . / 10, name = "EDF"))
plot_edf
```

### Single Factor Analysis - Bivariate - Expected Default Frequency
```{r, echo = FALSE}
plot_edf_scatter <- plot(EDF_group$EDF, EDF_group$default_rate,
                    xlab="EDF ", ylab="Default rate", pch=19) +
  abline(lm(EDF_group$default_rate~EDF_group$EDF), col="red")
plot_edf_scatter
```

### Single Factor Analysis - Bivariate - GDP_growth
GDP_growth is a variable common to all debtors dependent on year and country
```{r}
GDP_group <- Data %>% group_by(Date_of_data,Country) %>%
  summarise(default_rate = mean(Default),GDP_growth = mean(GDP_growth))
print(GDP_group, digits = 3, row.names = FALSE)
```

### Single Factor Analysis - Bivariate - GDP_growth - UK
```{r, echo = FALSE}
GDP_group_UK <- subset(GDP_group, Country %in% c("UK"))
ggplot(data=GDP_group_UK, aes(x=Date_of_data, y=default_rate, group=1)) +
  geom_point()+
  geom_line(aes(x=Date_of_data, y=GDP_growth / 5, group=1), col="Red")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . * 5, name = "GDP_Growth"))
```

### Single Factor Analysis - Bivariate - GDP_growth - FR
```{r, echo = FALSE}
GDP_group_FR <- subset(GDP_group, Country %in% c("FR"))
ggplot(data=GDP_group_FR, aes(x=Date_of_data, y=default_rate, group=1)) +
  geom_point()+
  geom_line(aes(x=Date_of_data, y=GDP_growth / 5, group=1), col="Red")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . * 5, name = "GDP_Growth"))
```

### Single Factor Analysis - Bivariate - GDP_growth - DE
```{r, echo = FALSE}
GDP_group_DE <- subset(GDP_group, Country %in% c("DE"))
ggplot(data=GDP_group_DE, aes(x=Date_of_data, y=default_rate, group=1)) +
  geom_point()+
  geom_line(aes(x=Date_of_data, y=GDP_growth / 5, group=1), col="Red")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . * 5, name = "GDP_Growth"))
```

### Single Factor Analysis - Bivariate - GDP_growth - PL
```{r, echo = FALSE}
GDP_group_PL <- subset(GDP_group, Country %in% c("PL"))
ggplot(data=GDP_group_PL, aes(x=Date_of_data, y=default_rate, group=1)) +
  geom_point()+
  geom_line(aes(x=Date_of_data, y=GDP_growth / 5, group=1), col="Red")+
  geom_line() +
  geom_point()+
  scale_y_continuous(name = waiver(),
                     sec.axis = sec_axis(~ . * 5, name = "GDP_Growth"))
```

### Single Factor Analysis - Bivariate - GDP_growth - All countries
```{r, echo = FALSE}
plot_gdp_scatter <- plot(GDP_group$GDP_growth, GDP_group$default_rate,
                    xlab="GDP_growth ", ylab="Default rate", pch=19) +
  abline(lm(GDP_group$default_rate~GDP_group$GDP_growth), col="red")
plot_gdp_scatter
```

### Final dataset
```{r}
Drivers_final <- Drivers_3[, c("Country_PL","Industry_AB",
                "Length_of_business","Total_assets","Credit_limit",
                "EDF","GDP_growth","Default")]
print(head(Drivers_final,5), digits = 2, row.names = FALSE)
```

# 3. Data split

### Development sample
  + Data that we use to estimate model parameters
  + Usually between 75% and 90% of the whole sample
```{r}
set.seed(101)
sample = sample.split(Drivers_final$Default, SplitRatio = .80)
development_sample = subset(Drivers_final, sample == TRUE)
```

### Hold-out sample
  + Data that we use to evaluate the performance of the model
  + Usually between 10% and 25% of the whole sample
```{r}
hold_out_sample  = subset(Drivers_final, sample == FALSE)
```

# 4. Model functional form

### Model functional form

Possible methods for PD modelling:

  + Probit model
  + Logistic regression
  + Scoring models
  + Machine learning
  + Neural networks
  
### Logistic Regression
\[ \ln \left\{ \frac{P[Y=1|X]}{P[Y=0|X]} \right\} = \beta_0 + X\beta \]
with $X = (X_1, X_2, \ldots, X_N)$ the set of prognostic factors.
Assuming a linear model for $f_n$, the probability that $Y=1$ is modelled as:
  \[y = \frac{1}{1+e^{-(\beta_0+\beta_1 x_1+\beta_2 x_2+\beta_3 x_3+\ldots)}}\]
In R, this regression can be fitted with the function \tt{glm()}.

# 5. Multiple Factor Analysis

### Number of possible models

+ We have 7 input variables (risk drivers) and 1 modelled variable
+ The number of possible models:
$2^7 - 1 = 127.$
```{r}
variables = colnames(Drivers_final)
variables
```

### Exemplary model
```{r, eval = FALSE}
m0 <- glm(data = development_sample,
          formula = Default ~ Country_PL + Industry_AB + 
                               Total_assets + Credit_limit + EDF,
         family = binomial)
summary(m0)[12]
```

### Exemplary model
```{r, echo = FALSE}
m0 <- glm(data = development_sample,
          formula = Default ~ Country_PL + Industry_AB + 
                               Total_assets + Credit_limit + EDF,
          family = binomial)
summary(m0)[12]
```

### Exemplary model
```{r, echo = FALSE}
est <- coefficients(m0)
expected_sign <- data.frame("Driver"=
                              c("Country_PL","Industry_AB","Total_assets","Credit_limit","EDF"),
                            "Sign" = c("-","+","-","-?","+?"), "Estimate" =
                              unname(est[c("Country_PL","Industry_AB","Total_assets","Credit_limit","EDF")]))
print(expected_sign, digits = 2)
```

### Acceptance criteria - No counterintuitive signs
```{r, echo = FALSE,fig.width=3,fig.height=2}
par(mfrow=c(1,2))
print(subset(expected_sign, Driver %in% ("Country_PL")), digits = 2)
plot_country
```

### Acceptance criteria - No counterintuitive signs
```{r, echo = FALSE,fig.width=3,fig.height=2}
par(mfrow=c(1,2))
print(subset(expected_sign, Driver %in% ("Industry_AB")), digits = 2)
plot_industry
```

### Acceptance criteria - No counterintuitive signs
```{r, echo = FALSE,fig.width=3,fig.height=2}
par(mfrow=c(1,2))
print(subset(expected_sign, Driver %in% ("Total_assets")), digits = 2)
plot_assets
```

### Acceptance criteria - No counterintuitive signs
```{r, echo = FALSE,fig.width=4.5,fig.height=2}
par(mfrow=c(1,2))
print(subset(expected_sign, Driver %in% ("Credit_limit")), digits = 2)
plot_limit
```

### Acceptance criteria - No counterintuitive signs
```{r, echo = FALSE,fig.width=3,fig.height=2}
par(mfrow=c(2,2))
print(subset(expected_sign, Driver %in% ("EDF")), digits = 2)
plot_edf
```

### Acceptance criteria - p-value
```{r}
summary <- data.frame(coef(summary(m0))[,c(1,4)])
summary$p_val_less_5PRC <- summary[,2] <= 0.05
summary
```

### Acceptance criteria - correlation
No two variables can be correlated more than 0.50 in absolute terms.
```{r}
corr_data <- subset(development_sample,
                    select = c("Country_PL",
                               "Industry_AB",
                               "Total_assets",
                               "Credit_limit",
                               "EDF"))
correlation_results <- cor(corr_data)
```

### Acceptance criteria - correlation
```{r, echo = FALSE}
print(correlation_results, digits=2)
```

### Acceptance criteria - Summary
  + Expected sign
    + Credit_limit and EDF do not meet the criteria
  + Significance (p-value)
    + Credit_limit and EDF do not meet the criteria
  + Correlation
    + Total_assets and Credit_limit cannot appear in the same model
    
Result -> model rejected

### Model search

An estimation is done for each possible model and only the models that fulfil all the criteria are considered further.
In practice:

  + models including correlated pairs of variables are not estimated
  + regulatory requirements state that some kinds of variables need to be included, eg:
    + customer size or proxy
    + macroeconomic
    
# 6. Model selection

### Model selection - performance criteria

For all the models that passed the acceptance criteria we calculate some performance metrics eg.:

  + Gini coefficient - the higher the better
  + Akaike information criterion (AIC) - the lower the better
  
### AIC - Akaike Information Criteria

$$ AIC = 2k - 2ln(\hat{L}),$$
where:

$k$ - number of parameters (penalize more parameters)

$\hat{L}$ - likelihood function (promote higher likelihood)
  
### Model selection - performance criteria

Let's compare three models:

  + m1: Default ~ Industry_AB + Length_of_business + Total_assets
  + m2: Default ~ Country_PL + Length_of_business + Total_assets
  + m3: Default ~ Country_PL + Industry_AB + Length_of_business + Total_assets
  
### Model selection - estimation of parameters
```{r}
m1 <- glm(data = development_sample,
          formula = Default ~ Industry_AB + Length_of_business +
                              Total_assets,
          family = binomial)
m2 <- glm(data = development_sample,
          formula = Default ~ Country_PL + Length_of_business +
                              Total_assets,
          family = binomial)
m3 <- glm(data = development_sample,
          formula = Default ~ Country_PL + Industry_AB +
                              Length_of_business + Total_assets,
          family = binomial)
```

### Model selection - Gini
We predict the probabilities for each model
```{r}
development_sample$prediction_m1 =
              fitted.values(m1)
development_sample$prediction_m2 =
              fitted.values(m2)
development_sample$prediction_m3 =
              fitted.values(m3)
```

### Model selection - Gini
```{r}
print(head(subset(development_sample, select =
                    c(Default,prediction_m1,
                      prediction_m2,prediction_m3)),
           10),digits = 2)
```

### Model selection - Gini
```{r}
model_summary <- data.frame(
              "Model"= c("m1","m2","m3"),
              "Gini_development" =
                c(Gini(development_sample$prediction_m1,
                        development_sample$Default),
                  Gini(development_sample$prediction_m2,
                        development_sample$Default),
                  Gini(development_sample$prediction_m3,
                        development_sample$Default)))
```

### Model selection - Gini
```{r}
print(model_summary, digits = 3)
```

### Model selection - AIC
```{r}
model_summary$AIC <- c(AIC(m1),AIC(m2),AIC(m3))
print(model_summary, digits = 3)
```

### Model selection - Champion and Challenger

After the analysis of all possible models for all functional forms considered we choose:

  + Champion model - best model (our m3)
  + Challenger model - second best (our m1)
  
# 7. Model validation

### Model validation
We need to check how our champion and challanger models perform on the hold-out sample
```{r}
hold_out_sample$prediction_m3 <-predict(m3,
                      newdata = hold_out_sample, type = 'response')
hold_out_sample$prediction_m1 <-predict(m1,
                      newdata = hold_out_sample, type = 'response')
```

### Validation - Gini
```{r}
validation_summary <- data.frame(
              "Model"= c("m3","m1"),
              "Gini_hold_out" =
                c(Gini(hold_out_sample$prediction_m3,
                      hold_out_sample$Default),
                  Gini(hold_out_sample$prediction_m1,
                      hold_out_sample$Default)))
```

### Validation - Gini
```{r}
print(validation_summary, digits = 3)
```

### Summarize
```{r}
summary_final <- merge(x = model_summary,
                       y = validation_summary,
                       by = "Model",
                       all.y = TRUE) %>% subset(select=-c(AIC))
summary_final$Dev_minus_hold_out <-
  summary_final$Gini_development - summary_final$Gini_hold_out
```

### Summarize
```{r}
print(summary_final, digits = 3)
```
### Conclusions
  + Both models seem to perform better on the hold-out sample than on the development sample
  + The classification remains the same:
    + Champion: m3 - Default ~ Country_PL + Industry_AB + Length_of_business + Total_assets
```{r}
print(coefficients(m3), digits = 3)
```

### Conclusions
  + Challenger: m1 - Default ~ Industry_AB + Length_of_business + Total_assets
```{r}
print(coefficients(m1), digits = 3)
```

### End
------------------------------------ THANK YOU!!! ------------------------------------ 